Nanophotonic computational design

### 2013-05-20 paper/export/paper.tex
Got the export to work.
Final update for paper.

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}
\input defs.tex
\begin{document}
\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\begin{abstract}
In contrast to designing nanophotonic devices 
    by tuning a handful of device parameters, 
    we have developed a computational method 
    which utilizes the full parameter space to design linear nanophotonic devices.
We show that our method may indeed be capable of designing 
    any linear nanophotonic device by demonstrating designed structures which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.
Critically, we show that our method 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, we are able to design devices 
    solely based on the user's desired performance specification for the device.
\end{abstract}
\ocis{230.75370, 130.3990.}

\begin{thebibliography}{99}
\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
%     nanophotonic circuits,''
%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
%     ``Active control of slow light on a chip with photonic crystal waveguides,''
%     Nature \textbf{438}, 65-69 (2005).
% \bibitem{slotfocus} M. Lipson, 
%     ``Guiding, modulating, and emitting light on 
%     silicon-challenges and opportunities,'' 
%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
%     C. Lagahe, and R. Baets, 
%     ``Electrically pumped InP-based microdisk lasers integrated with a 
%     nanophotonic silicon-on-insulator waveguide circuit,'' 
%     Opt. Express \textbf{15}, 6744-6749 (2007).
% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
%     ``Nanometre-scale germanium photodetector enhanced by a 
%     near-infrared dipole antenna,'' 
%     Nature Photonics \textbf{2}, 226-229 (2008).
% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% %     ``Nanotaper for compact mode conversion,'' 
% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% %     ``Adiabatic theorem and continuous coupled-mode theory for 
% %     efficient taper transitions in photonic crystals,''
% %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% %     ``Robust topology optimization of photonic crystal waveguides with 
% %     tailored dispersion properties.'' 
% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% %     \emph{Convex Optimization} 
% %     (Cambridge University Press, 2004)
% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
%     ``Inverse design of a three-dimensional nanophotonic resonator,''
%     Opt. Express \textbf{19}, 10563-10750 (2011). 
% \bibitem{veronis} G. Veronis, and S. Fan, 
%     ``Theoretical investigations of compact couplers between dielectric slab 
%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
%     Opt. Express \textbf{15}, 1211-1221 (2007).
% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

@@

For this reason, we have developed and implemented a computational method
    which is able to use the full parameter space 
    to design linear nanophotonic components in three dimensions.
Critically, our method requires no user intervention or manual tuning.
Instead, a \emph{design-by-specification} scheme is used 
    to produce designs based solely on a user's performance specification.

@@

Lastly, all our results are produced by simply specifying
    the functionality and performance of the desired device,
    which suggests that our method may indeed by able
    to design \emph{all} linear nanophotonic devices.

@@

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what we call an \emph{objective-first} \cite{ob1_wg}
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

@@

\subsection{Fiber couplers}
The capabilities of our method are further demonstrated
    in the design of nanophotonic fiber couplers,
    which couple light from an optical fiber at normal incidence
    into an in-plane waveguide\cite{baets}.

@@

\subsubsection{Fabrication-robustness of broadband wavelength splitter}
A analysis with regard to fabrication-error
    was also performed on the broadband wavelength splitter.
The specific fabrication error was a general over- or under-etch
    of the device (input and output waveguides unaffected).
\Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
    can be sustained before performance falls below 70\%, at the central
    operating wavelengths.
The structural variations at 8 nm of etch error are shown in \fig{top_wdm_overunder}.

@@

This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
\end{document}

>>>>

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}

\newcommand{\myfig}[2]{
    \begin{figure}[!h]
    \begin{centering}
    \includegraphics[width=0.8\textwidth]{#1}
    \caption{#2}\label{#1}
    \end{centering}
    \end{figure}
}

\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\eq}[1]{Eq.~\eqref{#1}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\newcommand{\BEAS}{\begin{eqnarray}}
\newcommand{\EEAS}{\end{eqnarray}}
% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
% \newcommand{\EEAS}{\end{IEEEeqnarray}}
\newcommand{\BSA}{\begin{subequations}\begin{align}}
\newcommand{\ESA}{\end{align}\end{subequations}}
\newcommand{\BE}{\begin{equation*}}
\newcommand{\EE}{\end{equation*}}
\newcommand{\BIT}{\begin{itemize}}
\newcommand{\EIT}{\end{itemize}}

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.} }

\DeclareMathOperator*{\minimize}{\text{minimize}\quad}
\newcommand{\subto}{\text{subject to}\quad}
\newcommand{\T}{^\dagger}

\newcommand{\ones}{\mathbf 1}
\newcommand{\reals}{{\mbox{\bf R}}}
\newcommand{\comps}{{\mbox{\bf C}}}
\newcommand{\integers}{{\mbox{\bf Z}}}
\newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices

\newcommand{\nullspace}{{\mathcal N}}
\newcommand{\range}{{\mathcal R}}
\newcommand{\Rank}{\mathop{\bf Rank}}
\newcommand{\Tr}{\mathop{\bf Tr}}
\newcommand{\diag}{\mathop{\bf diag}}
\newcommand{\lambdamax}{{\lambda_{\rm max}}}
\newcommand{\lambdamin}{\lambda_{\rm min}}

\newcommand{\Expect}{\mathop{\bf E{}}}
\newcommand{\Prob}{\mathop{\bf Prob}}
\newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
\newcommand{\dist}{\mathop{\bf dist{}}}
\newcommand{\argmin}{\mathop{\rm argmin}}
\newcommand{\argmax}{\mathop{\rm argmax}}
\newcommand{\epi}{\mathop{\bf epi}} % epigraph
\newcommand{\Vol}{\mathop{\bf vol}}
\newcommand{\dom}{\mathop{\bf dom}} % domain
\newcommand{\intr}{\mathop{\bf int}}

\begin{document}

\title{Nanophotonic computational design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Ginzton Laboratory, Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\begin{abstract}
In contrast to designing nanophotonic devices 
    by tuning a handful of device parameters, 
    we have developed a computational method 
    which utilizes the full parameter space to design linear nanophotonic devices.
We show that our method may indeed be capable of designing 
    any linear nanophotonic device by demonstrating designed structures which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.
Critically, we show that our method 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, we are able to design devices 
    solely based on the user's desired performance specification for the device.
\end{abstract}
\ocis{350.4238 (Nanophotonics); 350.3950 (Micro-optics).}

\begin{thebibliography}{99}
\bibitem{lipson} 
    A. Gondarenko and M. Lipson, 
    ``Low modal volume dipole-like dielectric slab resonator,'' 
    Opt. Express \textbf{16} 17689-17694 (2008).  
\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
\bibitem{levi}
    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
    ''Optimization of aperiodic dielectric structures,''
    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
    ``Design of robust and efficient photonic switches using topology optimization,''
    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
    153–165 (2012).
\bibitem{jameson} L. Martinelli and A. Jameson, 
    ``Computational aerodynamics: solvers and shape optimization,''
    J. Heat Transfer \textbf{135}, 011002 (2013).
\bibitem{bendsoe} M. P. Bendsoe and O. Sigmund,
    ``Material interpolation schemes in topology optimization,''
    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
\bibitem{ob1_wg} J. Lu and J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{miller} D. A. B. Miller, 
    ``All linear optical devices are mode converters,'' 
    Opt. Express \textbf{20}, 23985-23993 (2012).
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed optimization and statistical learning via the alternating direction method of multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{mode1} J. Castro, D. F. Geraghty, S. Honkanen, C. M. Greiner, D. Iazikov, and T. W. Mossberg, ``Demonstration of mode conversion using anti-symmetric waveguide Bragg gratings,'' Opt. Express \textbf{13}, 4180-4184 (2005).
\bibitem{mode2} E. Khoo, A. Liu, and J. Wu, ``Nonuniform photonic crystal taper for high-efficiency mode coupling,'' Opt. Express \textbf{13}, 7748-7759 (2005).
\bibitem{mode3} P. Sanchis, J. Marti, J. Blasco, A. Martinez, and A. Garcia, ``Mode matching technique for highly efficient coupling between dielectric waveguides and planar photonic crystal circuits,'' Opt. Express \textbf{10}, 1391-1397 (2002). 
\bibitem{forchel} T. D. Happ, M. Kamp, and A. Forchel, 
    ``Photonic crystal tapers for ultracompact mode conversion,'' 
    Opt. Lett. \textbf{26}, 1102-1104 (2001) 
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
\bibitem{robust1} F. Wang, J. S. Jensen, and O. Sigmund, ``Robust topology optimization of photonic crystal waveguides with tailored dispersion properties,'' J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011).
\end{thebibliography}

@@

To this end, increasingly sophisticated optimization strategies for 
    specific nanophotonic devices have been developed
    which are able to search this parameter space.
These range from the use of genetic algorithms\cite{lipson},
    level-set methods\cite{yablo}, 
    and the optimization of specific geometric parameters \cite{levi,johnson}.
Additionally, much success has been attained\cite{sigmund1}
    through the use of topological design methods that
    have traditionally been applied in other fields \cite{jameson,bendsoe}.

In this work, we have endeavored to extend the current art
    by developing and implementing a general computational method
    for nanophotonic design which extends across all linear nanophotonic devices.
Specifically, our method uses the full parameter space 
    to design linear nanophotonic components in three dimensions.
Critically, our method requires no user intervention or manual tuning.
Instead, a \emph{design-by-specification} scheme is used 
    to produce designs based solely on a user's performance specification.

@@

Lastly, all our results are produced by simply specifying
    the functionality and performance of the desired linear device
    in terms of mode conversion \cite{miller}.
The variety of successful designs presented 
    suggests that our method may indeed by able
    to design \emph{all} linear nanophotonic devices.

@@

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what we call an \emph{objective-first}\cite{ob1_wg}
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

@@

\subsection{Fiber couplers}
The capabilities of our method are further demonstrated
    in the design of nanophotonic fiber couplers,
    which couple light from an optical fiber at normal incidence
    into an in-plane waveguide \cite{baets}.

@@

\subsubsection{Fabrication-robustness of broadband wavelength splitter}
A analysis with regard to fabrication-error
    was also performed on the broadband wavelength splitter.
The specific fabrication error was a general over- or under-etch
    of the device (input and output waveguides unaffected) \cite{robust1}.
\Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
    can be sustained before performance falls below 70\%, at the central
    operating wavelengths.
The structural variations at 8 nm of etch error are shown in \fig{top_wdm_overunder}.

@@

\section{Acknowledgments}
This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
\end{document}

### 2013-05-20 paper/paper.tex
Final update for paper.

\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\eq}[1]{eq.~\eqref{#1}}
\newcommand{\fig}[1]{fig.~\ref{#1}}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\newcommand{\BEAS}{\begin{eqnarray}}
\newcommand{\EEAS}{\end{eqnarray}}
% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
% \newcommand{\EEAS}{\end{IEEEeqnarray}}
\newcommand{\BSA}{\begin{subequations}\begin{align}}
\newcommand{\ESA}{\end{align}\end{subequations}}
\newcommand{\BE}{\begin{equation*}}
\newcommand{\EE}{\end{equation*}}
\newcommand{\BIT}{\begin{itemize}}
\newcommand{\EIT}{\end{itemize}}

@@

\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\begin{abstract}
In contrast to designing nanophotonic devices 
    by tuning a handful of device parameters, 
    we have developed a computational method 
    which utilizes the full parameter space to design linear nanophotonic devices.
We show that our method may indeed be capable of designing 
    any linear nanophotonic device by demonstrating designed structures which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.
Critically, we show that our method 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, we are able to design devices 
    solely based on the user's desired performance specification for the device.
\end{abstract}
\ocis{230.75370, 130.3990.}

\begin{thebibliography}{99}
\bibitem{lipson} 
    A. Gondarenko, and M. Lipson, 
    ``Low modal volume dipole-like dielectric slab resonator,'' 
    Opt. Express \textbf{16} 17689-17694 (2008).  
\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
\bibitem{levi}
    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
    ''Optimization of aperiodic dielectric structures,''
    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
    ``Design of robust and efficient photonic switches using topology optimization,''
    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
    153–165 (2012).
\bibitem{jameson} L. Martinelli, and A. Jameson, 
    ``Computational Aerodynamics: Solvers and Shape Optimization,''
    J. Heat Transfer \textbf{135}, 011002 (2013).
\bibitem{bendsoe} M. P. Bendsoe, O. Sigmund,
    ``Material interpolation schemes in topology optimization,''
    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{miller} D. A. B. Miller, 
    ``All linear optical devices are mode converters,'' 
    Opt. Express \textbf{20}, 23985-23993 (2012).
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{mode1} J. Castro, D. F. Geraghty, S. Honkanen, C. M. Greiner, D. Iazikov, and T. W. Mossberg, ``Demonstration of mode conversion using anti-symmetric waveguide Bragg gratings,'' Opt. Express \textbf{13}, 4180-4184 (2005).
\bibitem{mode2} E. Khoo, A. Liu, and J. Wu, ``Nonuniform photonic crystal taper for high-efficiency mode coupling,'' Opt. Express \textbf{13}, 7748-7759 (2005).
\bibitem{mode3} P. Sanchis, J. Marti, J. Blasco, A. Martinez, and A. Garcia, ``Mode matching technique for highly efficient coupling between dielectric waveguides and planar photonic crystal circuits,'' Opt. Express \textbf{10}, 1391-1397 (2002). 
\bibitem{forchel} T. D. Happ, M. Kamp, and A. Forchel, 
    ``Photonic crystal tapers for ultracompact mode conversion,'' 
    Opt. Lett. \textbf{26}, 1102-1104 (2001) 
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
\bibitem{robust1} F. Wang, J. S. Jensen, and O. Sigmund, ``Robust topology optimization of photonic crystal waveguides with tailored dispersion properties,'' J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011).
\end{thebibliography}

@@

To this end, increasingly sophisticated optimization strategies for 
    specific nanophotonic devices have been developed
    which are able to search this parameter space.
These range from the use of genetic algorithms\cite{lipson},
    level-set methods\cite{yablo}, 
    and the optimization of specific geometric parameters\cite{levi,johnson}.
Additionally, much success has been attained\cite{sigmund1}
    through the use of topological design methods that
    have traditionally been applied in other fields\cite{jameson,bendsoe}.

@@

Lastly, all our results are produced by simply specifying
    the functionality and performance of the desired linear device
    in terms of mode conversion\cite{miller}.
The variety of successful designs presented 
    suggests that our method may indeed by able
    to design \emph{all} linear nanophotonic devices.

@@

\subsubsection{Fabrication-robustness of broadband wavelength splitter}
A analysis with regard to fabrication-error
    was also performed on the broadband wavelength splitter.
The specific fabrication error was a general over- or under-etch
    of the device (input and output waveguides unaffected)\cite{robust1}.
\Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
    can be sustained before performance falls below 70\%, at the central
    operating wavelengths.
The structural variations at 8 nm of etch error are shown in \fig{top_wdm_overunder}.

>>>>

\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\eq}[1]{Eq.~\eqref{#1}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\newcommand{\BEAS}{\begin{eqnarray}}
\newcommand{\EEAS}{\end{eqnarray}}
% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
% \newcommand{\EEAS}{\end{IEEEeqnarray}}
\newcommand{\BSA}{\begin{subequations}\begin{align}}
\newcommand{\ESA}{\end{align}\end{subequations}}
\newcommand{\BE}{\begin{equation*}}
\newcommand{\EE}{\end{equation*}}
\newcommand{\BIT}{\begin{itemize}}
\newcommand{\EIT}{\end{itemize}}

@@

\title{Nanophotonic computational design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Ginzton Laboratory, Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\begin{abstract}
In contrast to designing nanophotonic devices 
    by tuning a handful of device parameters, 
    we have developed a computational method 
    which utilizes the full parameter space to design linear nanophotonic devices.
We show that our method may indeed be capable of designing 
    any linear nanophotonic device by demonstrating designed structures which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.
Critically, we show that our method 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, we are able to design devices 
    solely based on the user's desired performance specification for the device.
\end{abstract}
\ocis{350.4238 (Nanophotonics); 350.3950 (Micro-optics).}

\begin{thebibliography}{99}
\bibitem{lipson} 
    A. Gondarenko and M. Lipson, 
    ``Low modal volume dipole-like dielectric slab resonator,'' 
    Opt. Express \textbf{16} 17689-17694 (2008).  
\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
\bibitem{levi}
    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
    ''Optimization of aperiodic dielectric structures,''
    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
    ``Design of robust and efficient photonic switches using topology optimization,''
    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
    153–165 (2012).
\bibitem{jameson} L. Martinelli and A. Jameson, 
    ``Computational aerodynamics: solvers and shape optimization,''
    J. Heat Transfer \textbf{135}, 011002 (2013).
\bibitem{bendsoe} M. P. Bendsoe and O. Sigmund,
    ``Material interpolation schemes in topology optimization,''
    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
\bibitem{ob1_wg} J. Lu and J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{miller} D. A. B. Miller, 
    ``All linear optical devices are mode converters,'' 
    Opt. Express \textbf{20}, 23985-23993 (2012).
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed optimization and statistical learning via the alternating direction method of multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{mode1} J. Castro, D. F. Geraghty, S. Honkanen, C. M. Greiner, D. Iazikov, and T. W. Mossberg, ``Demonstration of mode conversion using anti-symmetric waveguide Bragg gratings,'' Opt. Express \textbf{13}, 4180-4184 (2005).
\bibitem{mode2} E. Khoo, A. Liu, and J. Wu, ``Nonuniform photonic crystal taper for high-efficiency mode coupling,'' Opt. Express \textbf{13}, 7748-7759 (2005).
\bibitem{mode3} P. Sanchis, J. Marti, J. Blasco, A. Martinez, and A. Garcia, ``Mode matching technique for highly efficient coupling between dielectric waveguides and planar photonic crystal circuits,'' Opt. Express \textbf{10}, 1391-1397 (2002). 
\bibitem{forchel} T. D. Happ, M. Kamp, and A. Forchel, 
    ``Photonic crystal tapers for ultracompact mode conversion,'' 
    Opt. Lett. \textbf{26}, 1102-1104 (2001) 
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
\bibitem{robust1} F. Wang, J. S. Jensen, and O. Sigmund, ``Robust topology optimization of photonic crystal waveguides with tailored dispersion properties,'' J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011).
\end{thebibliography}

@@

To this end, increasingly sophisticated optimization strategies for 
    specific nanophotonic devices have been developed
    which are able to search this parameter space.
These range from the use of genetic algorithms\cite{lipson},
    level-set methods\cite{yablo}, 
    and the optimization of specific geometric parameters \cite{levi,johnson}.
Additionally, much success has been attained\cite{sigmund1}
    through the use of topological design methods that
    have traditionally been applied in other fields \cite{jameson,bendsoe}.

@@

Lastly, all our results are produced by simply specifying
    the functionality and performance of the desired linear device
    in terms of mode conversion \cite{miller}.
The variety of successful designs presented 
    suggests that our method may indeed by able
    to design \emph{all} linear nanophotonic devices.

@@

\subsubsection{Fabrication-robustness of broadband wavelength splitter}
A analysis with regard to fabrication-error
    was also performed on the broadband wavelength splitter.
The specific fabrication error was a general over- or under-etch
    of the device (input and output waveguides unaffected) \cite{robust1}.
\Fig{analysis_fab_shift2} reveals that up to 8 nm of over- or under-etching
    can be sustained before performance falls below 70\%, at the central
    operating wavelengths.
The structural variations at 8 nm of etch error are shown in \fig{top_wdm_overunder}.
